The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2014-01-02 main/s_background.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas

\begin{definition}
\label{def:equivalence}
%
\emph{Equivalence} of proofs in (cut-free, unit-only) multiplicative linear logic $(\perm)$ is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
%
\emph{\MLL\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
%
\end{definition}

@@

\end{itemize}
%
satisfying natural coherence conditions.
%
%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
%
The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
associativity is an identity by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.

>>>>

\begin{definition}
\label{def:equivalence}
%
\emph{Equivalence} of proofs $(\perm)$ in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
%
\emph{\MLL\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
%
\end{definition}

@@

\end{itemize}
%
satisfying natural coherence conditions.
%
%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
%
The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
associativity is an identity by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two term representations denote the same morphism.
